---
title: "Perform two-way Anova"
author: "Aniket Roy and Kruitk Shah"
date: "15/10/2020"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Example

Moth dataset are stored in csv file and then reading csv file to get data from csv file.
```{r,echo=TRUE}
data1 <- read.csv('moth.csv')
data1
```
``` {r,echo=TRUE}
data2<-data.frame("Moth"=data1[,1],"Position"=data1[,2],"lure"=data1[,3])
data2
```

## The hypothesis testing problem is:


**H0:There is no Significance difference between means of all**

**H1:There is a significant difference among means of all.**

*To check the normality of a data we have to do the shapiro test*

``` {r,echo=TRUE}
res <- shapiro.test(data2$Moth)
res

```
# Testing Normality Graphically

```{r,echo=TRUE}
qqnorm(data2$Moth)

```

**Bartlett's test is used to test if k samples have equal variances. Equal variances across samples is called homogeneity of variances.**

```{r,echo=TRUE}
bartlett.test(Moth~Position,data=data2)

bartlett.test(Moth~lure,data=data2)

```

Here in moth by position p-vlaue is 0.568 which is greater than 0.05 so we accept NULL Hypothesis.
And in moth by lure p-value is 0.8079 which is greater than 0.05 so we accept NULL Hypothesis.

```{r,echo=TRUE}
twoway <- aov(Moth~Position+lure,data=data2)
summary(twoway)
twoway
```

```{r,echo=TRUE}
TK <- TukeyHSD(twoway,"Position")
TK
plot(TK)

```