---
title: "Perform One-Way Anova"
author: "Aniket Roy and Krutik Shah"
date: "01/10/2020"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

------

```{r echo =TRUE}
data1 <- read.csv('One-Way(Rp).csv')
data1
```

## Performing One-Way Anova  
One-way ANOVA (Analysis of Variance) is used to examine the differences between means of more than two independent samples. It is used when we have a categorical independent variable (treatment) (with more than two categories) and a normally distributed interval or ratio dependent variable.  

H0:There is no difference between means of all three groups.  

Ha:Difference among maens is significant.  

## To Check Normality of data

```{r echo=TRUE}
result <- shapiro.test(data1$CBA)
result

result <- shapiro.test(data1$CS)
result

result <- shapiro.test(data1$BDA)
result
```

**As we can see that p-value of CBA,CS and BDA is as follows 0.06392,0.1133 and 0.4309.From this value we can say that all values are more than 0.05 so here We accept NULL Hypothesis.**

```{r echo=TRUE}
qqnorm(data1$CBA)
qqline(data1$CBA, distribution=qnorm)

qqnorm(data1$CS)
qqline(data1$CS, distribution=qnorm) 

qqnorm(data1$BDA)
qqline(data1$BDA, distribution=qnorm) 
```

## Testing Homogeneity of Variances  

**Bartlett's test is used to test if k samples have equal variances. Equal variances across samples is called homogeneity of variances.Before applying ANOVA we have to check the assumption about the homogeneity of variances.**  

```{r echo=TRUE}
result <- data.frame(data1$CBA,data1$CS,data1$BDA)
res.var <- bartlett.test(list(data1$CBA,data1$CS,data1$BDA))
res.var
```
As p value is greater than 0.05 .We fail to reject the null hypothesis H0 at 5%
level of significance. We conclude that the variances are equal across samples.

Homogeneity of variance is an assumption underlying both t tests and F tests (analyses of variance, ANOVAs) in which the population variances (i.e., the distribution, or “spread,” of scores around the mean) of two or more samples are considered equal.


## One Way Anova  

```{r echo=TRUE}
st_result <- stack(result)
res <- oneway.test(values~ind, data = st_result)
res
```
Since p-value which 0.03673 is very less than 0.05 we Accept the Null Hypothesis.


## Pair-wise Comparison  

```{r echo=TRUE}
res.anova <- aov(values~ind, data = st_result)
summary(res.anova)
TK <- TukeyHSD(res.anova)
TK
plot(TK)
```

## Linear Model  

```{r,echo="TRUE"}
model1 <- lm(values ~ ind,data=st_result)
anova(model1)

tk1 <- TukeyHSD(aov(model1))
tk1
plot(tk1)
```